{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-29 paper/paper.tex
s/probabilistic/nondeterministic
added rest of FSI-security

To reach this goal they model the scheduling explicit but general enough to apply
to a wide class of common schedulers. So rather than talking about program states,
they introduces system configurations which contain the list of threads the global
memory and the scheduler state. The scheduler is able to store information in its
state and can retrieve input (e.g. the number of active threads). Based on this
information the scheduler makes decisions. To cover probabilistic schedulers the
decision making of the scheduler and the execution of the program is probabilistic.

>>>>

To reach this goal they model the scheduling explicit but general enough to apply
to a wide class of common schedulers. So rather than talking about program states,
they introduces system configurations which contain the list of threads (thread pool) the global
memory and the scheduler state. The scheduler is able to store information in its
state and can retrieve input (e.g. the number of active threads). Based on this
information the scheduler makes decisions. To cover nondeterministic schedulers
(e.g. the uniform scheduler) the decision making of the scheduler and the execution
of the program is probabilistic.

Based on this scheduler model, a schedule-specific security property $\mathcal{S}$ is
defined on thread pools. Intuitively a thread pool is $\mathcal{S}$-secure if the
probability of running a program with system configuration $conf$ under the scheduler $\mathcal{S}$
results in the same global memory modulo low-equality as running the program with
system configuration $conf'$.

The novel security property introduced in this paper is defined without mentioning the
scheduler and equal to $\mathcal{S}$-security for a \textit{robust} scheduler $\mathcal{S}$.
Therefor this property is called \textit{flexible scheduler-independent security} (FSI-security).
A thread pool is FSI-secure if (starting from an low-equal memory configuration) the resulting
memories are always low-equal when executing commands that potentially modify low-variables and if
spawned threads are also FSI-secure.

Those robust schedulers are those, for which \textit{"the scheduling of low threads during a run of a FSI-secure
thread pool remains unchanged when one removes all high threads from the thread pool"}\cite{Mantel10}.

If a program is FSI-secure or not is checked statically with a security type system, which is introduced
for a sample while-language.
